Panel Seminars

### 2024-08-16 RDAtraitPredictionTutorial.Rmd
changed file path reference to first multivar figure
changed code so loading library code is visible
re-rendering site to have correct html for Katie's RDA page, since she published the link in PNAS

This tutorial accompanies the paper "The paradox of adaptive trait clines with non-clinal patterns in the underlying genes" published in PNAS [add link].

@@

```{r setup, eval=TRUE, echo=FALSE}

>>>>

[How to cite](https://marineomics.github.io/#How_to_Cite)

This tutorial accompanies the paper ["The paradox of adaptive trait clines with non-clinal patterns in the underlying genes"](https://doi.org/10.1073/pnas.2220313120) published in PNAS.

@@

```{r setup, eval=TRUE, echo=TRUE, message = FALSE, include = TRUE}

### 2024-08-16 index.Rmd
re-rendering site to have correct html for Katie's RDA page, since she published the link in PNAS

* [Choosing a population genomics sequencing approach](POP_01_choosing_population_genetics.html)  
* [Whole Genome Resequencing (WGS)](POP_04_WGS_intro.html)  
  * [Low coverage WGS](https://github.com/therkildsen-lab/genomic-data-analysis/blob/master/lcwgs_data_analysis.md)
* [Reduced Representation Sequencing](RADseq.html) 
* [Poolseq](POP_03_poolseq.html)
* [Redundancy Analysis (RDA) Trait Prediction](POP_05_RDAtraitPredictionTutorial.html)
* [PCA](POP_08_PCA.html)

>>>>

* [Choosing a population genomics sequencing approach](POP_01_choosing_population_genetics.html)  
* [Whole Genome Resequencing (WGS)](POP_04_WGS_intro.html)  
  * [Low coverage WGS](https://github.com/therkildsen-lab/genomic-data-analysis/blob/master/lcwgs_data_analysis.md)
* [Reduced Representation Sequencing](RADseq.html) 
* [Poolseq](POP_03_poolseq.html)
* [Redundancy Analysis (RDA) Trait Prediction](RDAtraitPredictionTutorial.html)
* [PCA](POP_08_PCA.html)
